Races with hyper3 objects

### 2022-05-10 inst/race3.Rmd
typos
slight rewording and tidyup

(takes about 15 minutes to process)

@@

# Some simple cases

The simplest nontrivial case is three competitors with strengths
$a,a,b$ and finishing ordr $a\succ b\succ a$.  The likelihood
function would be

@@

@@

constructor_table_2021 <- jj[,-ncol(jj)]
constructor_table_2021[,1:10]
constructor_2021_table <- constructor_table_2021
```

@@

and see that there is (very) strong evidence to reject this null.
Further, we may test the hypothesis that the big four (viz Mercedies,
Ferrari, Red Bull Racing Honda, and McLaren-Mercedes) are equal:

>>>>

(takes about an hour to process)

@@

# Some simple cases: likelihood functions for order statistics with clones

Here I consider some order statistics with nontrivial maximum
likelihood Bradley-Terry strength.   The simplest nontrivial case is
three competitors with strengths $a,a,b$ and finishing order $a\succ
b\succ a$.  The likelihood function would be

@@

# Some simple cases: Fisher information for simple cases

(work in progress).

@@

constructor_table_2021 <- jj[,-ncol(jj)]
constructor_table_2021[,1:17]
constructor_2021_table <- constructor_table_2021
```

@@

and see that there is (very) strong evidence to reject this null.
Further, we may test the hypothesis that the big four (viz Mercedes,
Ferrari, Red Bull Racing Honda, and McLaren-Mercedes) are equal:
